This PDF is a Git Repository\\Containing its Own \LaTeX\ Source

### 2017-05-01 article.tex
Shrink the Soviet poster to smaller than 64k
Fixed an error printout
Moved the Russian text to a separate PDF to reduce PDF object size

\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel} %Last language is default and active.
\usepackage{graphicx}

@@

I hope you like Soviet holes, dear neighbor, because chasing this
rabbit might remind you of \foreignlanguage{russian}{Кольская}. If you
grew bored reading Tristram Shandy, it's safe to skip to the next
section, 'cause it's turtles all the way down.

\begin{center}
\includegraphics[width=0.5\hsize]{RazvodityeKrolikov}
\end{center}

>>>>

\usepackage{graphicx}

@@

I hope you like Soviet holes, dear neighbor, because chasing this
rabbit might remind you of \includegraphics{kolskaya}. If you
grew bored reading Tristram Shandy, it's safe to skip to the next
section, 'cause it's turtles all the way down.

\begin{center}
%%\includegraphics[width=0.5\hsize]{RazvodityeKrolikov_small}
\end{center}
